### 2022-10-11 manuscript.Rmd
Add external code and plots to ms

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
knitr::read_chunk(here::here("R", "funs.R"))
knitr::opts_chunk$set(echo = TRUE)
builtin_source_hook <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  x <- grep("# HIDE$", x, invert = TRUE, value = TRUE)
  if (length(x) > 0) {
    return(builtin_source_hook(x, options))
  } else {
    invisible(NULL)
  }
})
```

@@

### 1.2.1	Statistical Power to Detect a Specific Effect of Interest
Central to many studies that employ SEM is the question of whether a specific parameter in a model (e.g., strength of a specific correlation or the slope parameter in a latent regression model) is different from a given value [e.g. @canada_2021]. Imagine that a researcher aims to test whether the correlation between two latent constructs significantly differs from zero. To this end, they would compare the model-fit between one model in which the correlation parameter is freely estimated and another model in which it is fixed to zero [@satorra_1985]. The corresponding null hypothesis in this case states that the parameter restrictions hold in the population. The difference in model fit will follow a $\chi^2$-distribution with degrees-of-freedom (*df*) equal to the difference of freely estimated parameters between the two models if the null hypothesis is true [@neale_2000; in this example *df* = 1, because only the correlation between the two latent factors is fixed in the restricted model]. If restricting the parameter of interest results in a significantly poorer model fit, this would suggest that the respective parameter indeed significantly differs from zero.
Following the logic outlined above, researchers can determine the statistical power for detecting a target effect in an SEM framework before conducting the study. A key aspect for this a-priori power calculation hinges on translating the differences in a specific parameter estimate into an effect size. Such translation can be achieved by investigating the discrepancy between the model-implied variance-covariance matrices associated with (1) the population model including the “true” parameter values and (2) the hypothesized model. The discrepancy between both matrices is quantified based on a specific fit function [for details on fit functions see @bollen_1989]. Recently, several user friendly tools have emerged that can guide modelers in quantifying effect sizes of a target effect to estimate statistical power in SEM [e.g. the R packages semPower @jobst_2021; or power4SEM @jak_2020 for analytical approaches; and the Shiny app pwrSEM @wang_2021; the interactive study planner tool LIFESPAN @brandmaier_2015;, or the R package simsem  @pornprasertmanit_2021 for simulation-based approaches]. As the investigation of a target effect practically translates into the comparison of nested models, researchers can in these cases analytically determine the statistical power and use this information for decisions on required sample size [@satorra_1985].

@@

```{r Figure1, fig.align = 'center', out.width= "100%", fig.cap = "Path diagrams of three competing SEMs on the structure of memory. Squares represent observed performance measures on the behavioral tasks. Circles represent latent constructs (PS = Pattern Separation, PC = Pattern Completion, GEN = Generalization). Single-headed arrows indicate regressions and double-headed arrows indicate covariances. See Buchberger et al., (2022) for in depth description of the models."}
knitr::include_graphics( "Images/Figure1.png")
```

@@

```{r Figure2, fig.align = 'center', out.width= "100%", fig.cap = "Schematic overview of the simulation process"}
knitr::include_graphics( "Images/Figure2.png")
```

@@

``` {r, results = 'hide', echo = TRUE}
model3 <-
  'ps       =~ task1 + task2 + task3 + task4 + task5 + task6
   pc       =~ task5 + task6 + task7 + task8 + task9
   gen      =~ task10+ task11 + task12 + task13'
```

@@

``` {r, eval = FALSE, echo = TRUE}
design <- createDesign(loading_strength = seq(0.5, 0.9, 0.1), 
                       samplesize       = seq(50, 200,5)
)
```

@@

### 2.1.3	Step 3: Generate 
Next, we define the mechanism to generate the synthetic data. An easy way to generating synthetic data within an SEM framework in R is the simulateData() function available in the lavaan package. Within the generate function, all parameters that are predetermined across iterations can be directly entered into the generating model syntax. However, all parameters that are supposed to be varied between different iterations of the simulation need to be accessed through the condition argument that is returned through the createDesign() function in step 2. Given our interests in the effect of loading strength and strength of covariance between the latent factors, we define these parameters in step 2 (Design) such that they can now be called via the condition argument in the generate function:

```{r generate, echo = TRUE}
```

Here, we define the generate function for the tripartite model. The factor loadings specified in step 2 (Design) are called from the condition argument such that they are varied across different iterations of the simulation, and are defined as a for syntax readability. For standardization purposes (that is, the total variance of each manifest variable summing up to 1), the loadings of indicators Task5 and Task6 are set to $\frac {a}{\sqrt{(2+2 \cdot cov1)}}$ to account for cross-loadings on multiple factors and are defined as b to ease syntax readability (cov1 = covariance between the latent factors pattern separation and pattern completion). The population model is defined by a model string, which specifies three latent factors (PS, PC, GEN), measured by the 13 manifest indicators (Task1 – Task13). The residual variances of the manifest variables are set to $1-a^2$ for standardization purposes. The covariance between the latent factors is set to the respective value from the condition argument. The data are simulated from the model syntax via the simulateData() function from the lavaan package and stored as dat. For the sake of clarity, all loadings and co-variances are spelled out separately (but see supplementary R code on github for rewriting the same model in a more concise syntax).

@@

### 2.1.4 Step 4: Analyze
In this step, we define the analyze function, which specifies how the data generated in step 3 should be analyzed. For the comparison of non-nested models, we rely on a combination of relative and absolute model fit parameters. We fit each of the competing models to each of the simulated data sets using the sem() function from the lavaan package and extract different measures of model fit using the helper function get_fitmeasures() (see funs.R in the supplementary material on github), namely the Comparative Fit Index [CFI, @bentler_1990], root mean square error of approximation [RMSEA, @steiger_2016] and the Bayesian Information Criterion [BIC, @raftery_1986]. The function returns the fit measures, the simulation model that was used in the respective iteration and information on model convergence. The analyze function for the example on memory composition could thus look like this: 
```{r analyze, echo = TRUE}
```
### 2.1.5	Step 5: Summarize
In step 5, we define how the results from the analyze step should be summarized. To this end, we extract how often the model used to generate the data (step 2) was actually recovered as the best fitting model. We implemented the following decision rules for identifying the best fitting model: (i) We define cut-off criteria for an adequate model fit according to established rules as CFI > .95 and RMSEA < 0.06 [@hu_1999]. (ii) Among the models that meet the cut-off criteria, we select the best fitting model for each data set based on the relative model fit (lowest BIC value). The goal of (i) and (ii) is to check whether the ground truth model that generated the data can be identified as the best fitting model in a given simulation run. For cases in which a given dataset does not converge for one of the models, we consider the outcome of these iterations as failing to recover the correct model. We summarize the proportion of successful model recovery for each combination of model parameters in the simulation separately. The summarize function that concatenates the results across simulation iterations for the example on the structure of memory in childhood could thus look like this:
```{r summarize, echo = TRUE}
```
First, the function restructures the results from the analyze function to obtain a tidy data frame with the fit measures for each model in a separate row. This data is then summarized for each iteration. The function identifies a) the ground truth model, that generated the data in this simulation iteration (sim_model) and b) the model which produced the best model fit (best). Here, the best model is defined as “0” if one of the three theoretical models did not converge, or if none of the models met the cut-off criteria as defined above. Otherwise, the best model is selected among the ones that met the cut-off criteria based on the relative model-fit.  The function returns the argument best_3, indicating how often across all iterations Model 3 was identified as the best fitting model, and best_sim, indicating how often the model that simulated the data was identified as the best fitting model (note that in the current analysis, both values are identical. Best_sim can however be useful to investigate Type-I error, see section 3.3).

@@

In a final step, we call the runSimulation() function from the simDesign package to execute the consecutive steps outlined above. Running the simulation for our example could look like this:

``` {r, results = 'hide', eval = FALSE, echo = TRUE}
results_cov_model3 <-
  runSimulation(
    design = design_cov_model3,
    replications = 10000,
    generate = generate_data,
    analyse = analyze_results,
    summarise = summarise_results,
    store_results = TRUE,
    parallel = TRUE,
    packages = c('SimDesign', 'lavaan', 'tidyverse'),
    fixed_objects = fixed_objects
  )
```

In this function, the pre-defined functions generate_data(), analyze_results() and summarise_results() are called. The number of replications is specified in the replications argument. To ensure a reasonable stability of the results, a sufficient number of replications is recommended. In our example, we simulated 10,000 datasets per condition. This leads to a standard error of the simulated power of less than 0.5%. The store_results argument can be used to store the individual results generated by the summarize function, allowing users to investigate the outcome on every iteration (in this example, the data frame containing all fit measures and convergence information for each iteration). Note however, that storing the individual results increases computation time and size of the resulting outcome arguments. The argument parallel can be used for parallel processing across multiple cores (e.g. when running the analysis on a computer cluster) to reduce computation time. If not specified otherwise, all available cores will be used per default when parallel = TRUE.

@@

In the example of comparing competing models of memory structure, we first examined the separability of the theoretical models by investigating the influence of the latent factors’ correlations on statistical power estimates. In our example simulation, we investigated the statistical power to retrieve Model 3 as the best fitting model, when it indeed generated the data, while varying sample sizes from 50 to 200 and factor inter-correlations from 0.1 to 0.9. In this case, we restricted the simulated correlations between the latent factors to positive values as there is no indication in the literature to suspect a negative relation among these memory capacities [e.g., @tucker-drob_2019]. Figure 3A displays the obtained power curves illustrating the estimated statistical power dependent on the total sample size and the factor inter-correlation. For this estimate, the loading of the manifest variables was fixed at 0.7 and the inter-correlation between all latent factors were varied simultaneously.

As expected, statistical power increased with increasing sample size. However, the separability of the latent factors mattered: The higher the correlations between factors, the less able we were to distinguish multi-factor models from a one-factor model. That is, the smaller the difference between competing models, the greater the sample size that would be required to dissociate between them with adequate power. For very high levels of inter-correlation (0.8 and higher) the increase of statistical power with increasing sample size was remarkably lower than for lower levels of inter-correlation (0.7 and below). When the inter-factor correlation was 0.9, not even a larger sample size (*N* =200) achieved an adequate level of power of 80%. These results are not surprising given that increasing the inter-correlations between the latent factors renders the models more similar to each other, and thus makes their distinction more challenging. For moderate levels of inter-correlation (<= 0.7) a statistical power of 95% was reached for *N* = 120.

@@

In a second step, we further examined the effect of the construct reliability on statistical power by investigating the loading strength of the manifest variables. To this end we conducted a second simulation following the steps outlined above while varying the sample size from 50 to 200 and the loadings of the manifest variables from 0.5 to 0.9. Figure 3B displays the obtained power curves, illustrating statistical power dependent on total sample size and loading strength of the manifest variables. For this estimate, the factor inter-correlation was set to 0.3. Again, increasing sample size lead to higher statistical power. However, the loading strength impacted estimates of statistical power: the higher the loadings of the manifest variables, the higher the statistical power achieved by a given sample size. For reasonably high levels of factor loadings (>= 0.7) a statistical power of 95% was reached for *N* = 120. 
# ```{r, echo= FALSE}
# source(here::here('02_create_plots.R'), local = knitr::knit_global())
# print(plot_load_model3)
# ```

@@

# INSERT FIGURE 4!
#```{r, echo= FALSE}
# source(here::here('02_create_plots.R'), local = knitr::knit_global())
# xxx
# ```  
The results of this analysis reveal that even for low levels of loadings strength (< 0.7), the probability of erroneously picking Model 3 as the best fitting model is reasonably low (< 7%). Likewise, this probability remains reasonably low for different levels of inter-factor correlations for all sample sizes (< 5%). Thus, in this specific model comparison Type-I error probability does not appear to be the main aspect driving sample size requirements for an informative research design.

## 3.4	Deriving a Sample Estimate From the Simulation Results

To derive a joint sample size estimate from the different parameters in the simulation, it is crucial to reiterate the theoretical assumptions on the strength of all parameters investigated in the simulation. In our illustration, it is reasonable to assume that the latent factors in the tri-partite model (Model 3, Figure 1) are only moderately correlated (below 0.7). Therefore, our model comparison requires a sample size of *N* = 120 to reach statistical power of 95% to adjudicate between the theoretical models, if the hypothesized model (Model 3) generates the data. We further assume that the manifest variables capture the latent constructs reasonably well — that is, exerting a loading strength of 0.7 or above. The results of the simulation suggest that *N* = 120 would suffice to achieve 95% with regard to the reliability of the manifest factors. In our example, the results of both analyses align, such that a sample size of *N* = 120 suffices to achieve a power of 95% regarding both the separability of the theoretical constructs and the reliability of the indicators. In cases where the derived sample estimate differs between the two analyses we suggest to derive the more conservative estimate of required sample size from the two simulations.
The results from the Type-I error analysis further indicate, that the probability of erroneously choosing an overly complex model is generally low. Therefore, the probability of committing a Type-I error for the sample size derived from the simulations on model separability and measurement reliability (*N* = 120) is negligible.

>>>>

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(ggpubr)
library(here)
library(SimDesign)

knitr::read_chunk(here::here("R", "funs.R"))
knitr::read_chunk(here::here("01_run_simulation.R"))
knitr::opts_chunk$set(echo = FALSE)

builtin_source_hook <- knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  x <- grep("# HIDE$", x, invert = TRUE, value = TRUE)
  if (length(x) > 0) {
    return(builtin_source_hook(x, options))
  } else {
    invisible(NULL)
  }
})
```

@@

### 1.2.1	Statistical Power to Detect a Specific Effect of Interest
Central to many studies that employ SEM is the question of whether a specific parameter in a model (e.g., strength of a specific correlation or the slope parameter in a latent regression model) is different from a given value [e.g. @canada_2021]. Imagine that a researcher aims to test whether the correlation between two latent constructs significantly differs from zero. To this end, they would compare the model-fit between one model in which the correlation parameter is freely estimated and another model in which it is fixed to zero [@satorra_1985]. The corresponding null hypothesis in this case states that the parameter restrictions hold in the population. The difference in model fit will follow a $\chi^2$-distribution with degrees-of-freedom (*df*) equal to the difference of freely estimated parameters between the two models if the null hypothesis is true [@neale_2000, in this example *df* = 1, because only the correlation between the two latent factors is fixed in the restricted model]. If restricting the parameter of interest results in a significantly poorer model fit, this would suggest that the respective parameter indeed significantly differs from zero.
Following the logic outlined above, researchers can determine the statistical power for detecting a target effect in an SEM framework before conducting the study. A key aspect for this a-priori power calculation hinges on translating the differences in a specific parameter estimate into an effect size. Such translation can be achieved by investigating the discrepancy between the model-implied variance-covariance matrices associated with (1) the population model including the “true” parameter values and (2) the hypothesized model. The discrepancy between both matrices is quantified based on a specific fit function [for details on fit functions see @bollen_1989]. Recently, several user friendly tools have emerged that can guide modelers in quantifying effect sizes of a target effect to estimate statistical power in SEM [e.g. the R packages semPower @jobst_2021; or power4SEM @jak_2020 for analytical approaches; and the Shiny app pwrSEM @wang_2021; the interactive study planner tool LIFESPAN @brandmaier_2015;, or the R package simsem  @pornprasertmanit_2021 for simulation-based approaches]. As the investigation of a target effect practically translates into the comparison of nested models, researchers can in these cases analytically determine the statistical power and use this information for decisions on required sample size [@satorra_1985].

@@

```{r Figure1, fig.align = 'center', out.width= "100%", fig.cap = "Path diagrams of three competing SEMs on the structure of memory. Squares represent observed performance measures on the behavioral tasks. Circles represent latent constructs (PS = Pattern Separation, PC = Pattern Completion, GEN = Generalization). Single-headed arrows indicate regressions and double-headed arrows indicate covariances. See Buchberger et al., (2022) for in depth description of the models."}
knitr::include_graphics( "Images/Figure1.pdf")
```

@@

```{r Figure2, fig.align = 'center', out.width= "100%", fig.cap = "Schematic overview of the simulation process"}
knitr::include_graphics( "Images/Figure2.pdf")
```

@@

```{r model3, echo = TRUE}
```

@@

```{r design_load_model3, echo = TRUE}
```

@@

### 2.1.3	Step 3: Generate 
Next, we define the mechanism to generate the synthetic data. An easy way to generating synthetic data within an SEM framework in R is the simulateData() function available in the lavaan package. Within the generate function, all parameters that are predetermined across iterations can be directly entered into the generating model syntax. However, all parameters that are supposed to be varied between different iterations of the simulation need to be accessed through the condition argument that is returned through the createDesign() function in step 2. Given our interests in the effect of loading strength and strength of covariance between the latent factors, we define these parameters in step 2 (Design) such that they can now be called via the condition argument in the generate function: 
```{r generate, echo = TRUE}
```

\textcolor{red}{here we now show the shortened original syntax. Is this understandable, or replace with simpler, longer function? (see original ms)}

Here, we define the generate function for the tripartite model. The factor loadings specified in step 2 (Design) are called from the condition argument such that they are varied across different iterations of the simulation, and are defined as a for syntax readability. For standardization purposes (that is, the total variance of each manifest variable summing up to 1), the loadings of indicators Task5 and Task6 are set to $\frac {a}{\sqrt{(2+2 \cdot cov1)}}$ to account for cross-loadings on multiple factors and are defined as b to ease syntax readability (cov1 = covariance between the latent factors pattern separation and pattern completion). The population model is defined by a model string, which specifies three latent factors (ps, pc, gen), measured by the 13 manifest indicators (task1 – task13). The residual variances of the manifest variables are set to $1-a^2$ for standardization purposes. The covariance between the latent factors is set to the respective value from the condition argument. The data are simulated from the model syntax via the simulateData() function from the lavaan package and stored as dat. For the sake of clarity, all loadings and co-variances are spelled out separately (but see supplementary R code on github for rewriting the same model in a more concise syntax).

@@

### 2.1.4 Step 4: Analyze
In this step, we define the analyze function, which specifies how the data generated in step 3 should be analyzed. For the comparison of non-nested models, we rely on a combination of relative and absolute model fit parameters. We fit each of the competing models to each of the simulated data sets using the sem() function from the lavaan package and extract different measures of model fit using the helper function get_fitmeasures() (see funs.R in the supplementary material on github), namely the Comparative Fit Index [CFI, @bentler_1990], root mean square error of approximation [RMSEA, @steiger_2016] and the Bayesian Information Criterion [BIC, @raftery_1986]. The function returns the fit measures, the simulation model that was used in the respective iteration and information on model convergence. The analyze function for the example on memory composition could thus look like this: 
```{r analyze, echo = TRUE}
```

### 2.1.5	Step 5: Summarize
In step 5, we define how the results from the analyze step should be summarized. To this end, we extract how often the model used to generate the data (step 2) was actually recovered as the best fitting model. We implemented the following decision rules for identifying the best fitting model: (i) We define cut-off criteria for an adequate model fit according to established rules as CFI > .95 and RMSEA < 0.06 [@hu_1999]. (ii) Among the models that meet the cut-off criteria, we select the best fitting model for each data set based on the relative model fit (lowest BIC value). The goal of (i) and (ii) is to check whether the ground truth model that generated the data can be identified as the best fitting model in a given simulation run. For cases in which a given dataset does not converge for one of the models, we consider the outcome of these iterations as failing to recover the correct model. We summarize the proportion of successful model recovery for each combination of model parameters in the simulation separately. The summarize function that concatenates the results across simulation iterations for the example on the structure of memory in childhood could thus look like this:
```{r summarize, echo = TRUE}
```
First, the function restructures the results from the analyze function to obtain a tidy data frame with the fit measures for each model in a separate row. This data is then summarized for each iteration. The function identifies a) the ground truth model, that generated the data in this simulation iteration (sim_model) and b) the model which produced the best model fit (best). Here, the best model is defined as “0” if one of the three theoretical models did not converge, or if none of the models met the cut-off criteria as defined above. Otherwise, the best model is selected among the ones that met the cut-off criteria based on the relative model-fit.  The function returns the argument best_3, indicating how often across all iterations Model 3 was identified as the best fitting model, and best_sim, indicating how often the model that simulated the data was identified as the best fitting model (note that in the current analysis, both values are identical. Best_sim can however be useful to investigate Type-I error, see section 3.3).

@@

In a final step, we call the runSimulation() function from the simDesign package to execute the consecutive steps outlined above. Running the simulation for our example could look like this:
```{r run_simulation_cov_model3, eval = FALSE, echo = TRUE}
```
In this function, the pre-defined functions generate_data(), analyze_results() and summarise_results() are called. The number of replications is specified in the replications argument. To ensure a reasonable stability of the results, a sufficient number of replications is recommended. In our example, we simulated 10,000 datasets per condition. This leads to a standard error of the simulated power of less than 0.5%. The store_results argument can be used to store the individual results generated by the summarize function, allowing users to investigate the outcome on every iteration (in this example, the data frame containing all fit measures and convergence information for each iteration). Note however, that storing the individual results increases computation time and size of the resulting outcome arguments. The argument parallel can be used for parallel processing across multiple cores (e.g. when running the analysis on a computer cluster) to reduce computation time. If not specified otherwise, all available cores will be used per default when parallel = TRUE.

@@

In the example of comparing competing models of memory structure, we first examined the separability of the theoretical models by investigating the influence of the latent factors’ correlations on statistical power estimates. In our example simulation, we investigated the statistical power to retrieve Model 3 as the best fitting model, when it indeed generated the data, while varying sample sizes from 50 to 200 and factor inter-correlations from 0.1 to 0.9. In this case, we restricted the simulated correlations between the latent factors to positive values as there is no indication in the literature to suspect a negative relation among these memory capacities [e.g., @tucker-drob_2019]. Figure 3A displays the obtained power curves illustrating the estimated statistical power dependent on the total sample size and the factor inter-correlation. For this estimate, the loading of the manifest variables was fixed at 0.7 and the inter-correlation between all latent factors were varied simultaneously.  
As expected, statistical power increased with increasing sample size. However, the separability of the latent factors mattered: The higher the correlations between factors, the less able we were to distinguish multi-factor models from a one-factor model. That is, the smaller the difference between competing models, the greater the sample size that would be required to dissociate between them with adequate power. For very high levels of inter-correlation (0.8 and higher) the increase of statistical power with increasing sample size was remarkably lower than for lower levels of inter-correlation (0.7 and below). When the inter-factor correlation was 0.9, not even a larger sample size (*N* =200) achieved an adequate level of power of 80%. These results are not surprising given that increasing the inter-correlations between the latent factors renders the models more similar to each other, and thus makes their distinction more challenging. For moderate levels of inter-correlation (<= 0.7) a statistical power of 95% was reached for *N* = 120.

@@

In a second step, we further examined the effect of the construct reliability on statistical power by investigating the loading strength of the manifest variables. To this end we conducted a second simulation following the steps outlined above while varying the sample size from 50 to 200 and the loadings of the manifest variables from 0.5 to 0.9. Figure 3B displays the obtained power curves, illustrating statistical power dependent on total sample size and loading strength of the manifest variables. For this estimate, the factor inter-correlation was set to 0.3. Again, increasing sample size lead to higher statistical power. However, the loading strength impacted estimates of statistical power: the higher the loadings of the manifest variables, the higher the statistical power achieved by a given sample size. For reasonably high levels of factor loadings (>= 0.7) a statistical power of 95% was reached for *N* = 120.

```{r, echo = FALSE, fig.width=11.3, fig.height=4.3, fig.align = 'center', fig.cap = "Simulation results: Estimated statistical power for recovering the data-generating model, i.e. Model 3 (y-axis) as a function of sample size (x-axis) with varying the factor inter-correlations when the loading strength was fixed to 0.7 (A) $;$ and with varying the loading strength when the factor inter-correlation was fixed to 0.3 (B). For each combination of parameters, 10,000 datasets were simulated. The red dashed horizontal line positioned at 95\\% discovery rate reflects the cut-off for identifying the appropriate sample size. The syntax to generate these plots with ggplot() can be found in the supplementary R Code on github"}

theme_plots <- theme(
  panel.background = element_blank(),
  panel.grid.major = element_line(color = "grey95"),
  legend.key       = element_rect(fill = NA),
  axis.line        = element_line(
    colour = "black",
    size = 0.5,
    linetype = "solid"
  ),
  axis.text.x      = element_text(
    size = 16,
    family = "sans",
    hjust = 0.5,
    vjust = -0.5
  ),
  axis.text.y      = element_text(
    size = 16,
    family = "sans",
    hjust = 0,
    vjust = 0.5
  ),
  axis.title.x     = element_text(
    size = 20,
    hjust = 0.5,
    vjust = -0.5
  ),
  axis.title.y     = element_text(
    size = 20,
    hjust = -0.1,
    vjust = 0.5
  ),
  plot.title       = element_text(
    lineheight = .8,
    face = "bold",
    size = 22
  ),
  legend.title     = element_text(size = 20),
  legend.text      = element_text(size = 18),
  legend.position  = "right"
)

results_load_model3 <-
  readRDS(here::here("results_load_model3.rds"))
results_cov_model3  <- readRDS(here::here("results_cov_model3.rds"))

plot_cov_model3 <- results_cov_model3 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    size = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('A \n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    size = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('B \n') +
  scale_color_discrete('loading       \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

joined_plot <-
  ggarrange(plot_cov_model3,
            plot_load_model3,
            ncol = 2,
            nrow = 1)
joined_plot
```

@@

```{r, echo = FALSE, fig.align='center', fig.height=8., fig.width=11.3, fig.cap = "Simulation results: Probability to erroneously pick Model 3 as the best fitting model when indeed Model 1 (A1) or Model 2 (A2/B2) generated the data, as a function of total sample size (x-axis) and the loadings strength of the manifest variables (A1/A2) or the strength of the covariance of the latent factors (B2). Note that the y-axis reaches from 0 to 20\\% for the sake of visibility."}

results_load_model1 <-
  readRDS(here::here("results_load_model1.rds"))
results_load_model2 <-
  readRDS(here::here("results_load_model2.rds"))
results_cov_model2  <- readRDS(here::here("results_cov_model2.rds"))
results_load_model3 <-
  readRDS(here::here("results_load_model3.rds"))
results_cov_model3  <- readRDS(here::here("results_cov_model3.rds"))

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(samplesize, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B1 \n') +
  scale_color_discrete('inter-factor \ncovariance') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

joined_plot <-
  ggarrange(
    plot_load_model1,
    NULL ,
    plot_load_model2,
    plot_cov_model2,
    ncol = 2,
    nrow = 2
  )
joined_plot

```

The results of this analysis reveal that even for low levels of loadings strength (< 0.7), the probability of erroneously picking Model 3 as the best fitting model is reasonably low (< 7%). Likewise, this probability remains reasonably low for different levels of inter-factor correlations for all sample sizes (< 5%). Thus, in this specific model comparison Type-I error probability does not appear to be the main aspect driving sample size requirements for an informative research design. 
## 3.4	Deriving a Sample Estimate From the Simulation Results
To derive a joint sample size estimate from the different parameters in the simulation, it is crucial to reiterate the theoretical assumptions on the strength of all parameters investigated in the simulation. In our illustration, it is reasonable to assume that the latent factors in the tri-partite model (Model 3, Figure 1) are only moderately correlated (below 0.7). Therefore, our model comparison requires a sample size of *N* = 120 to reach statistical power of 95% to adjudicate between the theoretical models, if the hypothesized model (Model 3) generates the data. We further assume that the manifest variables capture the latent constructs reasonably well — that is, exerting a loading strength of 0.7 or above. The results of the simulation suggest that *N* = 120 would suffice to achieve 95% with regard to the reliability of the manifest factors. In our example, the results of both analyses align, such that a sample size of *N* = 120 suffices to achieve a power of 95% regarding both the separability of the theoretical constructs and the reliability of the indicators. In cases where the derived sample estimate differs between the two analyses we suggest to derive the more conservative estimate of required sample size from the two simulations.
The results from the Type-I error analysis further indicate, that the probability of erroneously choosing an overly complex model is generally low. Therefore, the probability of committing a Type-I error for the sample size derived from the simulations on model separability and measurement reliability (*N* = 120) is negligible.
